Combined Task and Motion Planner through an Interface Layer

### 2015-05-13 documentation/ps4.tex
edits to final paper

We ran our test scenarios on the Baxter robot [Fig. \ref{fig:baxter}], designed by Rethink Robotics. 
Baxter is a humanoid robot with two 7 degree of freedom arms. 
Our tests used only the right arm with two finger gripper.

@@

When an action is infeasible because an object is blocking another object, the interface layer updates the state and calls the task planner. 
The interface layer, as described above, determines a list of obstructing objects.
The state update function goes through a section of a high level plan, performing all of the actions and updating the current state of the world.
Once the state update function reaches the step where the tryRefine function failed, the state update function adds predicates to the state describing which blocks obstruct other blocks.
The state function updates each action based on the preconditions and postconditions of each action: it confirms that all of the preconditions are satisfied and then adds true postconditions and removes falsified postconditions.

@@

@@

The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.  
For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.

@@

\subsection{Square Grid}
We ran the square grid scenario on a simulated Baxter robot.
The planner took approximately an hour to find a feasible plan. 
In simulation, Baxter successfully moves blocks to reach the target center block and places the center block on the target surface.
A video of the successful test trial in simulation can be found at [TODO: link here].

\subsection{Sorting}
We ran the sorting task in simulation and on the physical Baxter robot.
The planner took approximately an hour to find a feasible plan. 
We ran many test trials to achieve a successful run because the system was open-loop with respect to the environment.
It had feedback on the world position of the arms, but not on the position of the arms relative to the objects. This mean that drift accumulated over time.
Baxter successfully sorts green, red, and blue blocks into different bins. 
A video of the successful test trial can be found at \url{http://youtu.be/445_t_lUBdU}.

@@

[1] J. Hoffmann, B. Nebel. ``The FF planning system: fast plan generation through heuristic search''. J. Artif. Int. Res. 14, 1, 253-302, 2001.

>>>>

We ran our test scenarios on the Baxter robot [Fig. \ref{fig:baxter}], designed by Rethink Robotics. 
Baxter is a humanoid robot with two 7 degree of freedom arms. 
Our tests used only the right arm with the two finger gripper.

@@

When an action is infeasible because an object is blocking another object, the interface layer updates the state and calls the task planner. 
The interface layer, as described above, determines a list of obstructing objects.
The state update function goes through a section of a high level plan, performing all of the actions and updating the current state of the world.
Once the state update function reaches the step where the TryRefine function failed, the state update function adds predicates to the state describing which blocks obstruct other blocks.
The state function updates each action based on the preconditions and postconditions of each action: it confirms that all of the preconditions are satisfied and then adds true postconditions and removes falsified postconditions.

@@

For the sorting task, the PUTDOWN pose generator behaves slightly differently, since objects are dropped into bins rather than placed.
In this case, the pose generator had a fixed specified location to drop the object and had no randomization.

@@

The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.  
For our version of the algorithm, every time a new partial plan is generated, we first try to instantiate it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.

@@

\subsection{Square Grid}
We ran the square grid scenario on a simulated Baxter robot.
The planner took approximately an hour to find a feasible plan. 
In simulation, Baxter successfully moves blocks to reach the target center block and places the center block on the target surface.
A video of the successful test trial in simulation can be found at [TODO: link here].  We did not run this test on the real Baxter robot.

\subsection{Sorting}
We ran the sorting task in simulation and on the physical Baxter robot.
The planner took approximately twenty minutes to find a feasible plan. 
We ran many test trials to achieve a successful run because the system was open-loop with respect to the environment.
It had feedback on the world position of the arms, but not on the position of the arms relative to the objects. This mean that drift accumulated over time.
Additionally, the Baxter arm is shaky, and without very much room for error in the motion plans, Baxter sometimes hit adjacent objects due to wobbling outside of the planned motion.
Baxter successfully sorts green, red, and blue blocks into different bins. 
A video of the successful test trial can be found at \url{http://youtu.be/445_t_lUBdU}.

@@

\hspace{.25in}[1] J. Hoffmann, B. Nebel. ``The FF planning system: fast plan generation through heuristic search''. J. Artif. Int. Res. 14, 1, 253-302, 2001.
